
\questionheader{Buried treasure}

\Question\ Your Pacific Islands cruise has pulled up near a small but enticing island and
you and hundreds of other tourists have gone ashore for a day of sun, swimming and
scoffing ``authentic'' local foods and drinks. Tiring of the tourist traps, you wander off
the beaten path into the bush, where in addition to some peace and quiet, you find a scrap
of paper that happens to contain a map of the island and a promise of buried treasure! No
doubt it is fake, but with not much else to do until the dinghy returns you to the
floating RSL at 3.30\,pm, you might as well take a closer look.

The map divides the island neatly into square units. It has a list of N/S/E/W directions
listed, and you interpret that as taking a one-unit step in the specified direction.
So if you started at location $(4,6)$ and took steps ``N'', ``N'' and ``W'', you would end
up at location $(3,8)$.

Sometimes the direction given is the full word (North, South, East, West). Sometimes it is
the abbreviation (N, S, E, W). Capitalisation is always consistent. If you encounter any
instruction other than the eight specified then it is invalid.

So the question is: given a starting location and a list of directions, where might the
treasure be buried?

\Input From \IN\ you will your location and a list of directions.

\begin{itemize}
  \item The first line contains $X$, the $x$-value of your location.
  \item The second line contains $Y$, the $y$-value of your location.
  \item The third line contains $N$, the number of directions in the list.
  \item The next $N$ lines contain $D_i$, a direction that is either North, South, East,
    West, N, S, E, W or else it is an invalid direction.
\end{itemize}

Note that $X$ and $Y$ are integers such that $-1000 \le X,Y \le 1000$ and $N$ is an integer
such that $1 \le N \le 1000$.

\Output\ If all the directions are valid, you will output a single line $X'\ Y'$, being
your location after folloing the directions.

If you encounter an invalid direction, you will output the single line \texttt{Invalid
directions}.

\Sample

\minipagestwo{
  \sample{0.22}{8\\-7\\6\\N\\North\\W\\N\\East\\E\\S}
         {0.45}{9 -4}
}{
  \sample{0.22}{8\\-7\\6\\N\\North\\Go right\\N\\East\\E\\S}
         {0.47}{Invalid directions}
}

\Explanation\ In the first sample, the starting position is $(8,-7)$ and the sequence
$[N,N,W,N,\allowbreak E,E,S]$ results in a final position of $(9,-5)$. In the second
sample, the instruction \texttt{Go right} is invalid.

\Scratch\ You might like to run through the first sample on paper, completing a trace
table with columns $i$, $dir$, $X$, and $Y$.

