\questionheader{All Goes Wrong}

\Question\ Rebecca has to travel through a grid to her desgination, which is 3km
to the east and 3km to the north of her current position. John sends her $D$ directions
electronically. He uses:

\begin{itemize}
    \item N to indicate travel 1 kilometre to the north
    \item S to indicate travel 1 kilometre to the south
    \item E to indicate travel 1 kilometre to the east
    \item W to indicate travel 1 kilometre to the west
\end{itemize}

However, it is a complicated route. Further, there is a glitch in the system and
from some point all instructures from then on are reversed, with N becoming S, 
S becoming N, W becoming E, and E becoming W.

After how many instructions did the glitch occur?

\Input

The input is formatted as follows:
\begin{itemize}
    \item $D$, the number of directions being sent by John;
    \item $D$ lines of directions (either N, S, E or W) in the order sent by John.
\end{itemize}

You can be guaranteed that $D$ is a positive integer such that $D > 6$.

\Output\ You will write a single integer to \OUT, that being the number of instructions
after which the glitch occurred.

\Sample

\minipagestwo{%
  \sample{0.4}{16\\E\\E\\N\\W\\W\\W\\N\\W\\S\\W\\S\\W\\N\\N\\W}
         {0.4}{7} }{%
  \sample{0.4}{18\\W\\S\\S\\E\\W\\N\\E\\N\\S\\N\\N\\S\\E\\S\\W\\W\\W\\W}
         {0.4}{11} }

\Explanation In the first example, the glitch occurs after the 7th instruction.
This means that the correct sequence of instructions should have been:

EENWWWN\textcolor{red}{ENNENESSE}

This allows Rebecca to reach a position 3km east and 3km north of her starting point.

In the second example, the glitch occurs after the 11th instruction. In this case,
the correct sequence of instructions is:

WSSEWNENSNN\textcolor{red}{NWNEEEE}

Again, this would result in Rebecca reaching a position 3km east and 3km north of her starting point.

