
\questionheader{Don't touch the cracks}

\Question\ You are standing on an endless path made up of square tiles. A boring person
might simply walk along it without batting an eyelid. But you know that stepping on any of
the cracks between the tiles would simply be a crime.

Thus, you take steps in the following manner:
\begin{itemize}
  \item Most of the time, you take steps one tile at a time.
  \item But every 12 steps, you decide to perform a hop-skip-jump. This involves a hop on
    the same tile, a skip over the next tile, and a jump over the next three tiles. Each
    component of this hop-skip-jump counts as one step.
  \item Every 40 steps, you get tired - so you will pause and take a step back to the
    previous tile. If you happen to be in the middle of a hop-skip-jump or about to start
    one, the hop-skip-jump will be interrupted. You will not continue with an interrupted
    hop-skip-jump.
\end{itemize}

Your first step is on the first tile. How many steps will it take you to advance $N$
tiles?

\Input\ \IN\ contains a single positive integer $N$.

\Output\ You will write a single integer to \OUT: the total number of steps it will take
you to advance (at least) $N$ tiles.

\Sample

\minipagestwo{%
  \sample{0.2}{18}
         {0.2}{15}}{%
  \sample{0.2}{15}
         {0.2}{14}}

\Explanation In the first sample, you advance 11 tiles one step at a time. Then, on the
12th step, you begin the hop-skip-jump with a hop on the same tile. On the 13th step, you
skip over the next tile so that you have advanced 13 tiles so far. On the 14th step, you
jump over the next three tiles so that you have advanced 17 tiles so far. With one more
step (the 15th), you reach the target tile. Hence the answer is 15.

In the second sample, steps 1--12 are the same as before. On the 13th step, you have not
yet reached 15 tiles. However, on the 14th step when you jump over the next three tiles,
you land on the 17th tile. Therefore, it took you 14 steps to advance 15 tiles.
