
\questionheader{Underreporting}

\Question\ Yoanna manages a small taxi business. Drivers hire cars from her for a fee and
do their best to make a profit in the time they have the car. She runs the radio and
counts the cash. But lately she suspects that some drivers are underreporting their hours.
It's been pretty much an honesty system that's worked well so far, but she might need to
keep a closer eye on things.

Anyway, to help her get started, she wants you to find the number of drivers reporting
less than a certain amount of time per week. This won't prove anything, but it might tell
her who to watch out for.

\Input\

\begin{itemize}
  \item The first line contains two positive integers $N$ and $H$. $N$ is the number of
    lines of data that follow, and $H$ is the minimum number of hours considered
    acceptable for this investigation.
  \item Following that are $N$ lines of data, one for each driver. A line of data contains
    several positive integers, each representing the hours a driver reported on a day.
    There will be between 1 and 7 (inclusive) such numbers in a line, because this
    represents the last week's worth of data, but drivers don't necessarily take a car
    each day. You are interested in the \emph{total} of these hours.
\end{itemize}

\Output\ A single integer, being the number of drivers whose total hours are less than
$H$.

\Sample

\sample{0.3}{7 10\\5 8 3 5 3\\2 4 2\\6 6 6 6\\5 4 5 2 2 7\\1 2 3 4\\3 3 3\\3 5 3 4}
       {0.2}{2}

\Explanation\ The drivers' hours total to 24, 8, 24, 25, 10, 9, 15. Of these, two drivers
have a total that is less than the prescribed 10 hours, so the answer is \texttt{2}.

\Scratch\ Despite sounding complex, this question is very easy. You know how to read $N$
and $H$. You know how to read $N$ lines, and for each of those, you know how to turn it
into a list of integers. Now all you need is the \emph{sum} of the integers in each line,
and the built-in Python function \pycode|sum| has you covered. Try the following in your
console:

\begin{pythoncode}
  sum(4,5,1,2)
  hours = [5,4,5,2,2,7]
  sum(hours)
\end{pythoncode}

Line 1 shows that you can get the sum of several numbers given separately. Line 3 shows
that you can get the sum of the numbers in a list. So in this problem, you don't even need
to care how many numbers are on each line!
