
\chaptermacro{Document history}

{
\small

\newcommand{\versionmarker}[2]{\textbf{#1}\quad(#2)}
\newcommand{\versionmarkerspecial}[2]{{\color{BrickRed}\bfseries#1\quad(#2)}}

\versionmarker{0.2.4}{29 November 2021}
\begin{itemize}
  \item Small but important correction: 206 ``Buried treasure''. There was an error in the
    sample output.
\end{itemize}

\versionmarker{0.2.3}{26 July 2021}
\begin{itemize}
  \item Small but important correction: 204 ``Invite list''. There were two errors in the
    worked solution.
\end{itemize}

\versionmarker{0.2.2}{12 July 2021}
\begin{itemize}
  \item Three new exercises (by contributor Angeni Bai):
    \begin{itemize}
      \item Diamond Hands (Ch. 2)
      \item Don't touch the cracks (Ch. 3)
      \item Stairway to heaven (Ch. 5)
    \end{itemize}
\end{itemize}

\versionmarker{0.2.1}{6 July 2021}
\begin{itemize}
  \item New information box just after the title page: \emph{How to keep your book, code
    and data up to date}.
  \item Use of bit.ly URLS for book and code. Nicely formatted URLs too.
  \item Render the word learninformatics as \learninformatics{}.
  \item Small improvements to Introduction, removing needless footnotes.
\end{itemize}

\versionmarkerspecial{0.2}{5 July 2021}

This is a significant version (hence the move from 0.1 to 0.2) because of breaking changes
in Chapter~2. \textbf{Book 0.2} goes with \textbf{Software 2.0} and \textbf{Data 2.0}.
Note that only Chapters~1--2 have testing and judging data to support the exercises.

\begin{itemize}
  \item Chapter 2 is complete as it is intended for now, but\dots
  \item \dots exercises 203 \emph{Sum of squares}, 204 \emph{Check the invite list} and 206
    \emph{Buried treasure} were inserted, so current students may need to renumber a few
    of their exercise solutions.
  \item Two extra exercises at the end of Chapter 2: \emph{Even number in photos 1 \& 2}.
  \item \emph{High wire walk} moved from Chapter 2 to Chapter 5.
  \item A few extra problems added (either in full or sketches) in other chapters; no need
    to document them here.
  \item A variety of typo fixes, presentation fixes (especially tables), and incorrect
    data fixes.
  \item Pages are now numbered.
  \item Small update to Introduction regarding the commands used in the
    \textsf{learninformatics} environment.
\end{itemize}

\versionmarker{0.1.4}{30 June 2021}
\begin{itemize}
  \item Two new Chapter 5 (mixed) problems: \emph{Half-full flat white};
    \emph{One day I'll be rich}.
\end{itemize}

\versionmarker{0.1.3}{27 June 2021}
\begin{itemize}
  \item Included document history at end of book.
  \item Corrected function names in Chapters 5--6.
  \item Minor correction in output (Area calculator)
\end{itemize}

\versionmarker{0.1.2}{26 June 2021}
\begin{itemize}
  \item Changed title from ``Informatics for complete beginners'' to ``High School
    Informatics for complete beginners'' and adjusted title page, including colours.
  \item Three new problems in Chapter 5: \emph{Underreporting}; \emph{Sales stars};
    \emph{Percentage profit}.
\end{itemize}

\versionmarker{0.1.1}{24 June 2021}
\begin{itemize}
  \item A few notes added to Chapter 1 exercises to avert the kinds of problems students
    have encountered: one def inside another; how to print output on three separate lines;
    using a new variable to capture an intermediate result.
  \item Some prose improvement in Introduction.
  \item Problems added: \emph{Collatz} (1 and 2).
  \item More samples and explanation for \emph{High-wire act}.
  \item Corrected errors in some Chapter 1 output (including removing trailing zeros from
    floating-point numbers).
\end{itemize}

\versionmarker{0.1}{22 June 2021}
\begin{itemize}
  \item Initial version used by students.
\end{itemize}

}

